A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Add pattern table
Fix numbers of call sites

Table~\ref{table:site-package-summary} shows the number of call sites in
CRAN packages. 61 packages have a single call site, and one package has 142
call sites of \eval. 60 packages have no calls to \eval. The core packages
%%%% FIX THESE NUMBERS
have \miss{41} callsites of eval and Kaggle has none. These numbers are
under approximations as \eval may be called reflectively, through aliases,
or passed to a higher-order function.

>>>>

Table~\ref{table:site-package-summary} shows the number of call sites in
CRAN packages. 61 packages have a single call site, and one package, \emph{VGAM}, has \MaxCallSitePackage
call sites of \eval. \NoCallSitePackages packages have no calls to \eval. The core packages
have \NbCoreEvalCallSites call sites of \eval and Kaggle has none. These numbers are
under approximations as \eval may be called reflectively, through aliases,
or passed to a higher-order function.
